### 2017-11-16 paper/sections/1_introduction.tex
paper: add parameter sweeps for dynamically sized cache policy
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches extensively to improve performance
and resource utilization but the policies that guide what data to evict and
when to evict vary with the application or use case. For example, caching file
system metadata on both clients and servers reduces the number of remote
procedure calls and drastically improves the performance of create-heavy
workloads common in HPC~\cite{ren:sc2014-indexfs, patil:fast2011-giga+}. But
these techniques have policies, such as when to evict and what data to evict,
that are specific to the domain and application's behavior, so a new use case
may prove to be poor a match for the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using a data management language/policy engine and
arrive at a customized policy that works well for our target application.
Trying general policies and iterating to a very customized solution confirms
that our prototype can adapt to different types of workloads, but more
importantly, the collection of policies we developed were similar to policies
we designed for file system metadata load balancing, which suggests that there
are generalities in data management policy design that can be used across
domains.

>>>>

Storage systems use software-based caches extensively to improve performance
but the policies that guide what data to evict and when to evict vary with the
application or use case. For example, caching file system metadata on both
clients and servers reduces the number of remote procedure calls and
drastically improves the performance of create-heavy workloads common in
HPC~\cite{ren:sc2014-indexfs, patil:fast2011-giga+}. But these techniques have
policies for when to evict and what data to evict that are specific to the
application's behavior, so a new use case may prove to be poor a match for the
selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using a data management language/policy engine and
arrive at a customized policy that works well for our target application.
Trying general policies and iterating to a very customized solution confirms
that our prototype can adapt to different types of workloads, but more
importantly, the collection of policies we developed were similar to policies
we designed for file system metadata load balancing, which suggests that there
are generalities in data management policy design that can be used across
domains.

### 2017-11-16 paper/sections/4_dynamic-policies.tex
paper: add parameter sweeps for dynamically sized cache policy
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%\subsection{Trajectory Length}
%
%\subsection{Cloud Techniques: Elastic Search}
%
%What if we re-provision resources in response to events outside the
%application's control, such as a slow Lustre.
%
%\subsection{Future work}
%
%How Much: cache policy from past, regime detection, Belady's Min

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\

\caption{The performance and resource utilization trade-off for different cache
management policies. ``None" is ParSplice unmodified, ``Fixed Sized Cache"
limits the size of the cache by evicting the least recently used items, and
``Multi-Policy Cache" switches to a fixed sized cache after absorbing the
initial burstiness of the workload.  The size of the fixed sized cache for each
experiment is on the \(x\) axis.  \label{fig:methodology-tradeoff}}
\end{figure}
%
%\footnotesize \centering \begin{minted}[xleftmargin=3em,linenos]{lua} function
%when() if server[whoami]['cachesize'] > n then return true end return false
%end
%
%function howmuch() if servers[whoami]['cachesize'] > n return
%servers[whoami]['cachesize'] - n end return 0 end \end{minted} \caption{Policy
%that implements a basic LRU cache. The performance and memory utilization for
%different values of \(n\) are graphed in
%Figure~\ref{fig:methodology-tradeoff}.  \label{src:lru}} \end{figure}

@@

The results in Figure~\ref{fig:methodology-tradeoff} are slightly deceiving for
three reason: (1) segments take longer to generate later in the run, (2) the
memory footprint is the value at the end of 2.5 hours, and (3) this policy only
works well for the 2.5 hour run.  For (1), the curving down of the simulation
vs. wall-clock time is shown in Figure~\ref{fig:methodology-trajectory}; as the
nanoparticle grows it takes longer to generate segments so by the time we reach
2 hours, over 90\% of the trajectory is already generated.  For (2), the memory
footprint is around 0.4GB until we reach 100K key switch threshold. In
Figures~\ref{fig:methodology-tradeoff} we plot the final value. For (3),
Figure~\ref{fig:methodology-trajectory} shows that the cache fills up with 100K
keys at time 7200 seconds and its size is reduced to the size listed in the
legend.  The curves stay close to ``Unlimited" for up to an hour after the
cache is reduced but eventually flatten out as the persistent database gets
overloaded. 10K and 100K follow the ``Unlimited" curve the longest and are
sufficient policies for the 2.5 hour runs but anything longer would need a
different multi-policy cache management strategy.

\begin{figure}[t]
  \noindent\includegraphics[height=5cm,width=0.4\textwidth]{figures/methodology-trajectory.png}\\
  \caption{The rate that the trajectory is computed decays over time (which is
  expected) but this skews the performance improvements in the ``Multi-Part Policy" graph in 
  Figure~\ref{fig:methodology-tradeoff}. Our multi-policy cache management strategy works for 2.5
  hour jobs but not for 4 hour jobs.  \label{fig:methodology-trajectory}}
\end{figure}

@@

@@

>>>>

a\subsection{Trajectory Length}
%
%\subsection{Cloud Techniques: Elastic Search}
%
%What if we re-provision resources in response to events outside the
%application's control, such as a slow Lustre.
%
%\subsection{Future work}
%
%How Much: cache policy from past, regime detection, Belady's Min

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{The performance and resource utilization trade-off for different cache
management policies. ``None" is ParSplice unmodified, ``Fixed Sized Cache"
limits the size of the cache by evicting the least recently used items, and
``Multi-Policy Cache" switches to a fixed sized cache after absorbing the
initial burstiness of the workload.  The size of the fixed sized cache for each
experiment is on the \(x\) axis.  \label{fig:methodology-tradeoff}}
\end{figure}
%
%\footnotesize \centering \begin{minted}[xleftmargin=3em,linenos]{lua} function
%when() if server[whoami]['cachesize'] > n then return true end return false
%end
%
%function howmuch() if servers[whoami]['cachesize'] > n return
%servers[whoami]['cachesize'] - n end return 0 end \end{minted} \caption{Policy
%that implements a basic LRU cache. The performance and memory utilization for
%different values of \(n\) are graphed in
%Figure~\ref{fig:methodology-tradeoff}.  \label{src:lru}} \end{figure}

@@

The results in Figure~\ref{fig:methodology-tradeoff} are slightly deceiving for
two reasons: (1) segments take longer to generate later in the run and (2) the
memory footprint is the value at the end of 2.5 hours.  For (1), the trajectory
length vs vs.  wall-clock time curves down over time; as the nanoparticle grows
it takes longer to generate segments so by the time we reach 2 hours, over 90\%
of the trajectory is already generated.  For (2), the memory footprint is rises
until we reach 100K key switch threshold at 0.4GB, as shown by the
``\(\Delta_1\), Multi-Policy" curve in Figure~\ref{fig:memory-vs-time} but in
Figure~\ref{fig:methodology-tradeoff} we plot the final value. As a result, we
can only conclude that this policy only works well for this 2.5 hour run.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/dscache-vs-none.png}\\

\caption{The performance and resource utilization trade-off for the dynamically
sized cache (DSCache) policy compared to no cache management. With a negligible
performance impact, DSCache adjusts to different initial conditions
(\(\Delta\)) automatically and saves over 2\(\times\) memory in the best case.
\label{fig:dscache-vs-none}}
\end{figure}

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/memory-vs-time.png}\\

\caption{Memory utilization of different cache management policies.  ``No Cache
Management" allows unlimited cache growth, ``Multi-Policy" absorbs the initial
burstiness of the workload before switching to a more constrained cache, and
the ``Dynamic Policy" curves size the cache according to key access patterns.
We show a \(\Delta_2\) growth rate to demonstrate the dynamic policy's ability
to adjust to a different set of initial conditions.\label{fig:memory-vs-time}}
\end{figure}

@@

The performance and memory utilization is shown by the ``DSCache" bars in
Figure~\ref{dscache-vs-none.png}. Without sacrificing performance (trajectory
length), the dynamically sized cache policy uses between 32\%-66\% less memory
than the default ParSplice configuration (no cache management) for the 3
initial conditions we test. The memory usage is shown by the ``Dynamic Policy"
curves in Figure~\ref{figures/memory-vs-time.png}, where the behavior mirrors
the key access patterns in Figure~\ref{fig:keyspace-zoomed}.
